SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-25 2017-Xudong-SMT/ActaInformatica.tex
New proof for Th.2.

\begin{proof}

Intuitively, $\forall \ostate{\tilde{s}}\in\textit{Explored}=State(L)\text{, there must exist a transition}\ostate{\tilde{s_i}}\xrightarrow{v_i}\ostate{\tilde{s}}\text{ and }\forall \ostate{\tilde{s}}\in\textit{Explored}_{Smart}=State(L_{Smart})\text{, }\exists\ostate{\tilde{pre(s)}}\text{, }\ostate{\tilde{pre(s)}}\xrightarrow{v}\ostate{\tilde{s}}\text{ where \textit{Pred} is satisfiable and the state}\ostate{\tilde{pre(s)}}\text{ has two cases:}$
\begin{enumerate}
	\item[(1)] $\ostate{\tilde{pre(s)}}=\ostate{\tilde{s}}$
	\item[(2)] $\ostate{\tilde{pre(s)}}\in\textit{Explored}\text{-}\{\ostate{\tilde{s}}\}$
\end{enumerate}
By induction, there must exists a sequence $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s}}$ where all the $\textit{Pred}_i$ are satisfiable.

Then $\forall\ostate{\tilde{t}}\textit{Explored}=State(L)$, there are also two cases:
\begin{enumerate}
	\item[(1)] $\ostate{\tilde{t}}\in State(L1)$

	By definition of reachability, there exists a sequence $\ostate{\tilde{s_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where all the $\textit{Pred}_j$ are satisfiable.

	$\Rightarrow \ostate{\tilde{t}}\in State(L_{Smart})$
	\item[(2)] $\ostate{\tilde{t}}\in State(L)\text{-}State(L1)$, then $\forall \ostate{\tilde{u}}\in\textit{Explored}-\{\ostate{\tilde{t}}\}$,
	\begin{enumerate}
		\item[(1)] $\ostate{\tilde{u}}\in State(L)\text{-}State(L1)$.
		\item[(2)] $\ostate{\tilde{u}}\in State(L1)$, but there is no transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$.
		\item[(3)] $\ostate{\tilde{u}}\in State(L1)$, there exists transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$, but the $\textit{Pred}_u$ is unsatisfiable.
	\end{enumerate}
	By induction, there is no sequence from $\ostate{\tilde{s_0}}$ to $\ostate{\tilde{t}}$.

	$\Rightarrow \ostate{\tilde{t}}\notin State(L_{Smart})$
\end{enumerate}
Overall, $State(L1)$ is equal to $State(L_{Smart})$.
\end{proof}

>>>>

\begin{proof}
Let $L$, $L1$, $L_{Smart}$ respectively mean the result open transition set of original algorithm before pruning, original algorithm after pruning and smart algorithm. Similarly, $State(L)$, $State(L1)$, $State(L_{Smart})$ mean the result global state set of them. According to the algorithm, there has $L_{Smart}\in L$ and $State(L_{Smart})\in State(L)$.

Suppose that $f$: $State(L1)\rightarrow State(L_{Smart})$.
\begin{enumerate}
\setlength{\itemindent}{3.5em}
	\item[(Surjective)] If $\ostate{\tilde{s_0}}=Initial(p)$ then $f(\ostate{\tilde{s}})=\ostate{\tilde{t_0}}=Initial(p)$ must exists, the transitions started from them fulfill that
	\[\forall \ostate{\tilde{t_0'}}, \ostate{\tilde{t_0}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}\in L_{Smart},\quad \exists\ostate{\tilde{s'}},\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}\in L.\]
	The state $\ostate{\tilde{t'}}\in State(L_{Smart})$ and as $Pred_j$ of $\ostate{\tilde{t}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}$ is satisfiable, then if the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is also satisfiable, the state $\ostate{\tilde{s_0'}}$ is reachable in the original open automaton s.t. $\ostate{\tilde{s_0'}}\in State(L1)$, we can construct the mapping
	\[f(\ostate{\tilde{s_0'}})=\ostate{\tilde{t_0'}}.\]
	If the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s_0'}}\notin State(L1)$.

	Let $\textit{Explored}$, $\textit{Explored}_{Smart}$ respectively mean the explored states set of original algorithm and smart algorithm.

	Suppose that  $\ostate{\tilde{s}}\in \textit{Explored}$ there is $\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$ where $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$, there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$.

	The transitions $\ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}$ and $\ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}$ have several cases:
	\begin{enumerate}
		\item[(1)] $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$

		We can find that 
		 \[\exists\ostate{\tilde{s'}}\in \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}\quad where\quad f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
		\item[(2)] $\ostate{\tilde{t'}}\notin \textit{Explored}_{Smart}$

		There must has 
		\[\exists\ostate{\tilde{s'}}\notin \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}.\]
		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is satisfiable then there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$. So the $\ostate{\tilde{s'}}$ is reachable in the original open automaton, we can construct the mapping
		\[f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s'}}\notin State(L1)$.
	\end{enumerate}	
	Overall, \[\forall \ostate{\tilde{t}}\in State(L_{Smart}),\quad \exists\ostate{\tilde{s}}\in State(L1), f(\ostate{\tilde{s}})=\ostate{\tilde{t}}.\]
	\item[(Injective)] If there is a pair of states $\ostate{\tilde{s}} and \ostate{\tilde{t}}$ constructs the mapping $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$. We can know that $\ostate{\tilde{s}}\in \textit{Explored},\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$.

	As when there is $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$, the state is must be $\ostate{\tilde{s'}}\in \textit{Explored}$ where $f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}$.
	So it is a one-to-one mapping.
\end{enumerate}

Then as the function $f$ is both surjective and injective, it is a bijective function. The theorem is proved.

%Intuitively, $\forall \ostate{\tilde{s}}\in\textit{Explored}=State(L)\text{, there must exist a transition}\ostate{\tilde{s_i}}\xrightarrow{v_i}\ostate{\tilde{s}}\text{ and }\forall \ostate{\tilde{s}}\in\textit{Explored}_{Smart}=State(L_{Smart})\text{, }\exists\ostate{\tilde{pre(s)}}\text{, }\ostate{\tilde{pre(s)}}\xrightarrow{v}\ostate{\tilde{s}}\text{ where \textit{Pred} is satisfiable and the state}\ostate{\tilde{pre(s)}}\text{ has two cases:}$
%\begin{enumerate}
%	\item[(1)] $\ostate{\tilde{pre(s)}}=\ostate{\tilde{s}}$
%	\item[(2)] $\ostate{\tilde{pre(s)}}\in\textit{Explored}\text{-}\{\ostate{\tilde{s}}\}$
%\end{enumerate}
%By induction, there must exists a sequence $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s}}$ where all the $\textit{Pred}_i$ are satisfiable.
%
%Then $\forall\ostate{\tilde{t}}\textit{Explored}=State(L)$, there are also two cases:
%\begin{enumerate}
%	\item[(1)] $\ostate{\tilde{t}}\in State(L1)$
%	
%	By definition of reachability, there exists a sequence $\ostate{\tilde{s_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where all the $\textit{Pred}_j$ are satisfiable.
%	
%	$\Rightarrow \ostate{\tilde{t}}\in State(L_{Smart})$
%	\item[(2)] $\ostate{\tilde{t}}\in State(L)\text{-}State(L1)$, then $\forall \ostate{\tilde{u}}\in\textit{Explored}-\{\ostate{\tilde{t}}\}$,
%	\begin{enumerate}
%		\item[(1)] $\ostate{\tilde{u}}\in State(L)\text{-}State(L1)$.
%		\item[(2)] $\ostate{\tilde{u}}\in State(L1)$, but there is no transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$.
%		\item[(3)] $\ostate{\tilde{u}}\in State(L1)$, there exists transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$, but the $\textit{Pred}_u$ is unsatisfiable.
%	\end{enumerate}
%	By induction, there is no sequence from $\ostate{\tilde{s_0}}$ to $\ostate{\tilde{t}}$.
%	
%	$\Rightarrow \ostate{\tilde{t}}\notin State(L_{Smart})$
%\end{enumerate}
%Overall, $State(L1)$ is equal to $State(L_{Smart})$.
\end{proof}
